### 2016-11-07 oldmort.Rnw
new plots

\begin{enumerate}
\item \"elite, HISCLASS 1 and 2, Higher managers and higher professionals.
\item Lower managers and farmers, HISCLASS 3 and 8.
\item Lower professionals, HISCLASS 4, 5 and 6. Lower professionals, lower clerical, foremen.
\item Workers, HISCLASS 7, 9, 10, 11 and 12, Lower and unskilled workers (including farm workers).
%%\item Lower skilled farm workers, HISCLASS 10 and 12, Lower and unskilled farm workers
\end{enumerate}

@@

<<causes41>>=
cvb <- vb
cvb$event <- cvb$heart ## Can this be done better?
cvb <- cvb[!(cvb$period %in% c("1961-1970", "1971-1980")), ]
cvb$period <- factor(cvb$period)

@@

@@

<<causes12>>=
cvb <- vb
cvb$event <- cvb$cancer ## Can this be done better?
cvb <- cvb[!(cvb$period %in% c("1961-1970", "1971-1980")), ]
cvb$period <- factor(cvb$period)

>>>>

\begin{enumerate}
\item \'Elite, HISCLASS 1 and 2, Higher managers and higher professionals.
\item Lower managers and farmers, HISCLASS 3 and 8.
\item Lower professionals, HISCLASS 4, 5 and 6. Lower professionals, lower clerical, foremen.
\item Workers, HISCLASS 7, 9, 10, 11 and 12, Lower and unskilled workers (including farm workers).
%%\item Lower skilled farm workers, HISCLASS 10 and 12, Lower and unskilled farm workers
\end{enumerate}

@@

<<causes41>>=
cvb <- vb
cvb$event <- cvb$heart ## Can this be done better?
cvb <- cvb[!(cvb$period %in% c("1851-1875", "1876-1900")), ]
cvb$period <- factor(cvb$period)

@@

Models are fitted separately for each time period, from  1901 to
2013. We stratify on HISCLASS
and use the covariates {\tt sex}, {\tt   civst}, and {\tt urban}
(Skellefteå town or outside). The cumulative
hazards at the end of the time period (65 if 40--64, 90 if 65--89) are the
main target in our analysis: These numbers are used in the process of
graphically illustrating the development over time.

@@

<<causes12>>=
cvb <- vb
cvb$event <- cvb$cancer ## Can this be done better?
cvb <- cvb[!(cvb$period %in% c("1851-1875", "1876-1900")), ]
cvb$period <- factor(cvb$period)
